Software Citation Principles

### 2016-03-02 sc-principles/software-citation-principles.tex
moving note in intro and fixing to recognize what James has already added

@@

\katznote{add cites to James's study how what people cite software and Matthew Mayernik's similar one as part of motivation}

>>>>

\katznote{as part of motivation, James added cite to his study how what people cite software.  Dan to add cite of Matthew Mayernik's similar one, and perhaps trim text/table for space.}

@@
